---
title: "HW4"
author: "Tommy Cheng"
date: "October 8, 2016"
output: html_document
---

## Homework4
Problem1a: (1,2,3,...,19,20)
```{r}
a <- (1:20)
```

Problem1b: (20,19,...,2,1)
```{r}
b <- (20:1)
```

Problem1c: (1,2,3,...,19,20,19,18,...,2,1)	
```{r}
c(1:20,19:1)
```

Problem1d: (4,	6,	3)	and	assign	it	to	the	name	tmp.	
```{r}
tmp <- c(4,6,3)
```
Problem1e) (4,6,3, 4,6,3,...,4,6,3) where there are 10 occurrences of 4.
```{r}
rep(tmp,10)
```
Problem1f) (4,6,3,	4,6,3,...,4,6,3,4)	where	there	are	11	occurrences	of	4,	10	
occurrences	of	6	and	10	occurrences	of 3.	
```{r}
c( rep(tmp,10), 4)
```
Problem1g) (4,4,...,4,	6,6,...,6,	3,3,...,3)	where	there	are	10	occurrences	of	4,	20	
occurrences	of	6	and	30	occurrences	of	3.	
```{r}
c(rep(4,10), rep(6,20), rep(3,30))
```
Problem2) Create a vector of the	values of e^x
cos(x)	at	x	=	3,3.1,3.2,...,5.9,6.
```{r}
m <- seq(3,6,0.1)
exp(m)*cos(m)
```
Problem3a) Create a vector (0.1^3*0.2^1,0.1^6*0.2^4,0.1^9*0.2^7,...,0.1^36*0.2^34)
```{r}
x<-seq(3,36,3)
y<-seq(1,34,3)
v <- (0.1^x*0.2^y)
```
Problem3b) Create a vector (2,2^2/2,...2^25/25)
```{r}
(2^c(1:25))/c(1:25)
```
Problem4a) Find the sum of formula
```{r}
k <- c(10:100) #create vector with values from 10 to 100
sum(k^3+4*k^2) #sum of formula
```
Problem4b) Find the sum of formula
```{r}
r <-c(1:25) #create vector with values from 1 to 25
sum((2^r)/r + 3^r/(r^2))
```
Problem5a)Use function paste to create vectors of length 30. ("label 1", "label 2",....., "label 30"). with a single space between label and the number following.
```{r}
s1 <- c(1:30)
paste('label', s1, sep=" ")
```
Problem5b) ("fn1", "fn2", ..., "fn30"). In this case, there is no space between fn and the number 
```{r}
s2 <- c(1:30)
paste('fn', s2, sep="")
```
Problem6 create xVec and yVec
```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
```
Problem6a) Create the vector (y2-x1,y3-x2,...yn-xn-1)
```{r}
yVec[-1]-xVec[-250]
```
Problem6b) Create the vector(sin(y1)/cos(x2),...sin(yn-1))/cos(xn)
```{r}
sin(yVec[-250]) / cos(xVec[-1])
```
Problem6c) Create the vector (x1+2*x2-x3,...x(n-2)+2*x(n-1)-xn)
```{r}
xVec[-c(249,250)] + 2*xVec[-c(1,250)]-xVec[-c(1,2)]
```
Problem6d) Finds the sum of the formula
```{r}
sum(exp(-xVec[-1])/(xVec[-250]+10))
```
Problem7a) Pick	out	the	values in yVec which are greater than 600.
```{r}
yVec[yVec>600]
```
Problem7b) Pick out values in xVec which correspond to the values in yVec which are > 600 by index
```{r}
which(yVec>600)
```
Problem7c) Finds the values in xVec which correspond to values in yVec which are > 600?
```{r}
xVec[yVec>600]
```
Problem7d) Creates a vector
```{r}
(abs(xVec-mean(xVec)))^(1/2)
```
Problem7e) Finds how many values in yVec are within 200 of the max value
```{r}
length(which(yVec >= max(yVec)-200))
```
Problem7f) Finds how many values in xVec are divisible by 2. 
```{r}
length(which(xVec%%2==0))
```
Problem7g) Sorts the numbers in xVec in the order of increasing values in yVec
```{r}
xVec[order(yVec)]
```
Problem7h)
```{r}
yVec[seq(1,250,3)]
```
Problem8) By using the function cumprod	to calculate to sum of a formula
```{r}
1+sum(cumprod(seq(2,38,2)/seq(3,39,2)))
```

